Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

\begin{lemma}
	\label{lem:1req}
	In a~single repartitioning of nodes (after a~merge of components), \TAlg exchanges at most two pairs of nodes.
\end{lemma}

\begin{proof}
	If no component respecting partition exists after the merge of components, then \TAlg resets all components, ends the phase and performs no repartitioning.
	It suffices to show that the merged component has size at least $4$ to conclude that \TAlg incurs no cost.

@@

	If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the repartitioning is local within $U$ and $V$.
	In this case, a~local repartition is possible (within $U$ and $V$), for a~cost of at most $2$ swaps.
	If either $U$ or $V$ is of type $C_3$, a~component of size $3$ participates in a~merge, and we have a~component of size at least $4$, and \TAlg ends the phase with no repartitioning.

>>>>

\begin{lemma}
	\label{lem:1req}
	In a~single repartition of nodes (after a~merge of components), \TAlg exchanges at most two pairs of nodes.
\end{lemma}

\begin{proof}
	If no component respecting partition exists after the merge of components, then \TAlg resets all components, ends the phase and performs no migrations.
	It suffices to show that the merged component has size at least $4$ to conclude that \TAlg incurs no cost.

@@

	If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the repartitioning is local within $U$ and $V$, for the~cost of at most $2$ swaps.
	If either $U$ or $V$ is of type $C_3$, a~component of size $3$ participates in a~merge, and we have a~component of size at least $4$, and \TAlg ends the phase with no repartitioning.
